The \dealii{} Library, Version 8.5

### 2017-03-02 8.5/deal85.tex
initial paper
update

\hypersetup{
  pdfauthor={Wolfgang Bangerth, Timo Heister, Luca Heltai, Guido Kanschat,
    Martin Kronbichler, Matthias Maier, Bruno Turcksin
  %, Toby D. Young
  },
  pdftitle={The deal.II Library, Version 8.4, 2016},
}

@@

\title{The \dealii{} Library, Version 8.4}
\author[1]{Wolfgang Bangerth}
\affil[1]{Department of Mathematics, Texas A\&M University, College Station,
    TX 77843, USA,
    {\texttt{bangerth@math.tamu.edu}}}
\author[2]{Denis Davydov}
\affil[2]{Chair of Applied Mechanics, University of
    Erlangen-Nuremberg, Egerlandstr. 5, 91058 Erlangen, Germany,
  {\texttt{denis.davydov@fau.de}}}
\author[3]{Timo Heister}
\affil[3]{Mathematical Sciences,
  O-110 Martin Hall.
  Clemson University.
  Clemson, SC 29634, USA,
  {\texttt{heister@clemson.edu}}}
\author[4]{Luca Heltai}
\affil[4]{SISSA - International School for Advanced Studies, Via
  Bonomea 265, 34136 Trieste, Italy,
  {\texttt{luca.heltai@sissa.it}}}
\author[5]{Guido Kanschat}
\affil[5]{Interdisciplinary Center for Scientific Computing (IWR),
  Universit{\"a}t Heidelberg, Im Neuenheimer Feld 368, 69120 Heidelberg, Germany,
  {\texttt{kanschat@uni-heidelberg.de}}}
\author[6]{Martin Kronbichler}
\affil[6]{Institute for Computational Mechanics, Technical University of
  Munich, Boltzmannstr.~15, 85748 Garching,
  Germany,
  {\texttt{kronbichler@lnm.mw.tum.de}}}
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics, University of Minnesota, 127 Vincent Hall,
  206 Church Street SE, Minneapolis, MN 55455, USA,
  {\texttt{msmaier@umn.edu}}}
\author[8]{Bruno Turcksin}
\affil[8]{Department of Mathematics, Texas A\&M University, College Station,
  TX 77843, USA,
  {\texttt{turcksin@math.tamu.edu}}}
\author[9]{David Wells}
\affil[9]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA
  {\texttt{wellsd2@rpi.edu}}}
%\author[8]{Toby~D.~Young}
%\affil[8]{Institute of Fundamental Technological Research of the Polish
%  Academy of Sciences, ul. Pawi{\'n}skiego 5b, Warsaw 02-106, Poland,
%  {\texttt{tyoung@ippt.pan.pl}}}

@@

\begin{abstract}
  This paper provides an overview of the new features of the finite element
  library \dealii{} version 8.4.
\end{abstract}

@@

D.~Wells was partially supported by the National Science Foundation through
grant DMS-1344962.

@@

\bibliography{deal84}{}
\bibliographystyle{abbrv}

>>>>

\hypersetup{
  pdfauthor={Wolfgang Bangerth, Timo Heister},
  pdftitle={The deal.II Library, Version 8.5, 2016},
}

@@

\title{The \dealii{} Library, Version 8.5}
\author[1]{Wolfgang Bangerth}
\affil[1]{xxx,
    {\texttt{bangerth@math.tamu.edu}}}    
\author[2]{Timo Heister}
\affil[2]{Mathematical Sciences,
  O-110 Martin Hall.
  Clemson University.
  Clemson, SC 29634, USA,
  {\texttt{heister@clemson.edu}}}

@@

\begin{abstract}
  This paper provides an overview of the new features of the finite element
  library \dealii{} version 8.5.
\end{abstract}

@@

@@

\bibliography{paper}{}
\bibliographystyle{abbrv}
